---
output: pdf_document
---
# Research : What is Transmission Effects on Fuel Efficiency ?

Overview
========

You work for Motor Trend, a magazine about the automobile industry. Looking at a data set of a collection of cars, they are interested in exploring the relationship between a set of variables and miles per gallon (MPG) (outcome). They are particularly interested in the following two questions:

* "Is an automatic or manual transmission better for MPG"
* "Quantify the MPG difference between automatic and manual transmissions"

The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973-74 models).

Research Method
===============

The dataset contains of 32 rows on 11 variables name below :-

1. mpg: Miles per US gallon
2. cyl: Number of cylinders
3. disp: Displacement (cc)
4. hp: Raw Horsepower
5. drat: Rear axle ratio
6. wt: Weight (lb / 1000)
7. qsec: 1/4 mile time in sec
8. vs: V engine or Straight engine
9. am: Transmission (0 = automatic, 1 = manual)
10. gear: Number of gears
11. carb: Number of carburetors

Details records of the dataset

```{r}
unique(mtcars)
```

Research Questions
===============

* <b>"Is an automatic or manual transmission better for MPG"</b>


Summary for all cars

```{r}
summary(mtcars)
```

Summary for automatic type cars

```{r}
summary(mtcars[mtcars$am==0,])
```

Summary for manual type cars

```{r}
summary(mtcars[mtcars$am==1,])
```

We found that the mean for MPG for manual cars is bigger than automatic which is [ 24.39 > 17.15 ].
Further investigation needed to be done to verify this . 

* <b>"Quantify the MPG difference between automatic and manual transmissions"</b>

 
By plotting into BoxPlot we can have more info

```{r}
boxplot(mpg ~ am, data = mtcars, col=(c("gold","darkgreen")), 
        xlab = "Transmission Type", ylab = "MPG",
        main="MPG vs. Transmission Type")
```

it proves that manual = 1 transmission is higher mpg mean than automatic = 0

We need to do the hypothesis testing to prove this

```{r}
aggregate(mpg~am, data = mtcars, mean)
```

The mean transmission for manuals is 24.39 mpg which is 7.24 mpg higher than automatic which is 17.15 mpg

We want to test and to determine is there any significant between this. Student TTest can be used to achive this.

```{r}
a <- mtcars[mtcars$am == 0,]
m <- mtcars[mtcars$am == 1,]
t.test(a$mpg, m$mpg)

```

With the pValue = 0.001374 , we reject the NULL hypothesis. There is a difference between the mpg for auto and manual transmission.

We try to fit the data into the linear model to check the variance 

```{r}
m<-lm(mpg~am,data=mtcars)
summary(m)

```

We found that the R-Squared = 0.3598 , so we can assume the model only can be trusted for 36% of variance.

We also want to analyze the differences between the group means and their association.We put the dataset into the model and compared it with the Anova

```{r}
model <- lm(mpg~am + wt + hp + cyl, data = mtcars)
anova(m,model)

```

The model finally can be summarized below :- 

```{r}
summary(model)

```


Conclusion
===============

The model clearly explains with the 84.9%  of variance that on average the manual transmission will have more 1.47805 more mpg than the automatic transmission.

We also found that the residuals were normally distributed.

```{r}
plot(model)

```




