---
output: pdf_document
---
# Research : What is Transmission Effects on Fuel Efficiency ?

Overview
========

You work for Motor Trend, a magazine about the automobile industry. Looking at a data set of a collection of cars, they are interested in exploring the relationship between a set of variables and miles per gallon (MPG) (outcome). They are particularly interested in the following two questions:

* "Is an automatic or manual transmission better for MPG"
* "Quantify the MPG difference between automatic and manual transmissions"

The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973-74 models).

Research Method
===============

* Dataset Details

Summary for all cars

```{r}
summary(mtcars)
```

Summary for automatic type cars

```{r}
summary(mtcars[mtcars$am==0,])
```

Summary for manual type cars

```{r}
summary(mtcars[mtcars$am==1,])
```

```{r}
unique(mtcars)
```
The dataset contains of 32 rows on 11 variables name below :-

1. mpg: Miles per US gallon
2. cyl: Number of cylinders
3. disp: Displacement (cc)
4. hp: Raw Horsepower
5. drat: Rear axle ratio
6. wt: Weight (lb / 1000)
7. qsec: 1/4 mile time in sec
8. vs: V engine or Straight engine
9. am: Transmission (0 = automatic, 1 = manual)
10. gear: Number of gears
11. carb: Number of carburetors


Research Questions
===============

* <b>"Is an automatic or manual transmission better for MPG"</b>

We found that the mean for MPG for manual cars is bigger than automatic which is [ 24.39 > 17.15 ]. Further investigation need to be done to verify this . 
By plotting into BoxPlot we can have more info

```{r}
boxplot(mpg ~ am, data = mtcars, col=(c("gold","darkgreen")), 
        xlab = "Transmission Type", ylab = "MPG",
        main="MPG vs. Transmission Type")
```

it proves that manual = 1 transmission is higher mpg mean than automatic = 0


* <b>"Quantify the MPG difference between automatic and manual transmissions"</b>



